%-*- program: pdflatex -*-
%-*- program: bibtex -*-
%-*- program: pdflatex -*-
%-*- program: pdflatex -*-


% --------------------------------------------------------------
% Preamble
% --------------------------------------------------------------

\documentclass[english,natbib,man,floatsintext,mask]{apa6}
% \usepackage{arxiv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{url}            % simple URL typesetting
\usepackage{hyperref}       % hyperlinks
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\usepackage{booktabs}       % professional-quality tables
\usepackage{tabularx}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{gensymb}        % degree, angle symbols

% for math equations and symbols
\usepackage{amsmath} 
\usepackage{amssymb} 
\newcommand{\E}{\mathbb{E}}
\newcommand{\SD}{\mathit{SD}}
\newcommand{\SE}{\mathit{SE}}
\newcommand{\BF}{\mathit{BF}}
\DeclareMathOperator\arctanh{arctanh}

% This prevents placing floats before a section.
\usepackage{placeins}

% bibliography
% \usepackage{natbib}

% allows for floats when doing jou or doc style
\usepackage{graphicx}      
\graphicspath{{./figs/}}  
%\usepackage{float}

% for long tables
\usepackage{longtable}

% linenumbers
\usepackage[mathlines]{lineno}

% in APA man mode captions are too large
% making sure they are reasonable
\usepackage{setspace}
% \usepackage[font=singlespacing]{caption}
% \captionsetup{font=singlespacing}

%%% some support for commenting

\usepackage{color}
\definecolor{Blue}{RGB}{0,0,255}
\definecolor{Red}{RGB}{255,0,0}
\newcommand{\jo}[1]{\textcolor{Red}{[Jacob: #1]}}  
\newcommand{\hs}[1]{\textcolor{Blue}{[Hrvoje: #1]}} 
% \newcommand{\jo}[1]{}  
% \newcommand{\hs}[1]{} 

%%% commands for help with reviews

% marking the reviewer comments
\newcommand\eatpunct[1]{}
\newcommand{\com}[2][]{\vspace{5mm}\paragraph[ ]{ \eatpunct}\label{#1}\emph{#2}\vspace{5mm}}

% \par\refstepcounter{paragraph}\paragraphmark{#1}

% marking the changes in the main text
% for hyperlinks, see: https://tex.stackexchange.com/questions/129541/hyperref-and-lineno-always-jumping-to-first-page
\newcommand{\llabel}[1]{\hypertarget{llineno:#1}{\linelabel{#1}}}
\renewcommand{\lineref}[1]{\hyperlink{llineno:#1}{\ref*{#1}}}
\newcommand{\chg}[2]{\llabel{#1}\textcolor{Red}{ #2}} 
\newcommand{\quotetext}[1]{\vspace{2mm}\noindent \hangindent=-2cm \hangafter=0 ``#1''\vspace{2mm}}


% ---------------------------------------------------------
% Title, authors
% ---------------------------------------------------------

\title{The visual environment and attention in decision making}

\shorttitle{The visual environment and attention in decision making}

\threeauthors{Jacob L. Orquin*}{Erik S. Lahm}{Hrvoje Stojić}
\threeaffiliations{Aarhus University and Reykjavik University}{Aarhus University}{University College London}

%This description should be included within the manuscript on the abstract/keywords page.

\authornote{Jacob L. Orquin and Erik S. Lahm, Department of Management/MAPP, Aarhus University, Fuglesangs alle 4, 8210 Aarhus V - Denmark; Hrvoje Stojić, Max Planck UCL Centre for Computational Psychiatry and Ageing Research, University College London, 10-12 Russell Square, London, WC1B 5EH, United Kingdom. The authors thank Martin Meissner, Tobias Otterbring, Sonja Perković, and Valdimar Sigurdsson. This research was supported by the Independent Research Fund Denmark, grant number: 8046-00014A and the Lundbeckfonden, grant number R281-2018-27. \\ 
Data Availability Statement. The data and code reported in the manuscript is made available at Open Science Framework at \url{https://osf.io/buk7p/} \citep{orquin2020osfa}. \\
*Correspondence concerning this article should be addressed to Jacob L. Orquin, Department of Management/MAPP, Aarhus University, Fuglesangs alle 4, 8210 Aarhus V - Denmark. E-mail: jalo@mgmt.au.dk.}

%\rightheader{Orquin, Lahm, Stojic}
%\leftheader{The visual environment and attention in decision making}


% ---------------------------------------------------------
% Abstract
% ---------------------------------------------------------

\abstract{% limit: 250 words
Visual attention is a fundamental aspect of most everyday decisions, and governments and companies spend vast resources competing for the attention of decision makers. In natural environments, choice options differ on a variety of visual factors, such as salience, position, or surface size. However, most decision theories ignore such visual factors, focusing on cognitive factors such as preferences as determinants of attention. \chg{}{To provide a systematic review of how the visual environment guides attention we meta-analyze 122 effect sizes on eye movements in decision making. The psychometric meta-analysis and $Top10$ sensitivity analysis show that visual factors play a similar or larger role than cognitive factors in determining attention. The visual factors that most influence attention are positioning information centrally, $\rho = .43$ $(Top10 = .67)$, increasing the surface size, $\rho = .35$ $(Top10 = .43)$, reducing the set size of competing information elements, $\rho = .24$ $(Top10 = .24)$, and increasing visual salience, $\rho = .13$ $(Top10 = .24)$. Cognitive factors include attending more to preferred choice options and attributes, $\rho = .36$ $(Top10 = .31)$, effects of task instructions on attention, $\rho = .35$ $(Top10 = .21)$, and attending more to the ultimately chosen option, $\rho = .59$ $(Top10 = .26)$.} Understanding real-world decision making will require integration of visual and cognitive factors in future theories of attention and decision making.}
% limit: 5 keywords
\keywords{eye movements, decision making, attention, meta-analysis, visual environment, cognitive factors} 


% ---------------------------------------------------------
% Text
% ---------------------------------------------------------

\begin{document}
% \raggedbottom

\input{reviews}

% original part
\linenumbers
\maketitle

\section{\normalfont\normalsize Public significance statement}
\noindent Visual attention in decision making is influenced by the relevance of information and by how information is presented i.e., visual factors like the position, salience, and size of information and the number of competing information elements. We show that \textit{how} information is presented is more important to attention than the relevance of the information. Policy makers and companies can leverage visual factors to mislead or guide our attention to information that enhances welfare supporting behaviors.\par
\newpage

\input{introduction}
\input{method}
\input{results}
\input{discussion}


%\subsection{Author contributions}

%JLO and ESL developed the study concept. ESL performed the literature search. JLO and ESL coded the studies. JLO and HS performed the analyses. JLO, ESL, and HS wrote the manuscript. 


% -----------------------------------------------------------
% Bibliography
% -----------------------------------------------------------

\bibliographystyle{apalike}
\bibliography{references.bib}
\clearpage


% -----------------------------------------------------------
% Appendix
% -----------------------------------------------------------

\appendix
\input{appendix}

\end{document}